\documentclass[12pt]{scrartcl}
\usepackage{blubird}
% has options [nodate, nosans, nofancy, nocolor, code]

% box setup - should be moved to somewhere nicer
\mdfsetup{
	roundcorner = 2pt,
	linewidth = 1pt,
	innertopmargin = 0.5em,
	innerbottommargin = 1em,
	frametitlefont = \bfseries,
}

% TITLE 
\title{Complex Analysis Notes}
\author{Bryan Lu}
\date{December 2021 - January 2022} % do not use if [nodate] option enabled
 
\begin{document}
\maketitle

\setcounter{section}{-1}
\section{Foreword}
These are notes for the FA21 MATH 2230 study group for complex analysis over break. These are intended as a summary of the material presented in Stein-Shakarchi and Ahlfors, with supplements from Chapter V of \textit{Advanced Mathematical Techniques for Scientists and Engineers} by Osborne.

Complex analysis is a wonderful subfield of analysis and is useful for a lot of math/physics majors! It's relatively independent from the study of real analysis, and arguably (in my opinion) it's a lot more fun and elegant than its real counterpart! :)

Some prerequisites -- if you've taken MATH 2230 at Cornell, this should be accessible to you. Otherwise, the prerequisites are an interest in rigor, and some level of mathematical sophistication, i.e. some exposure to real analysis, particularly in regards to limits, continuity, and differentiation, and of course at least some familiarity with manipulating complex numbers. Some basic notions will be skimmed over here, as... well... it's really very similar to analysis in $\RR^2$ in this respect so we skim over it with the intention of  focusing on the highlights instead.

Many of the earlier diagrams in these notes are courtesy of Mathematica -- it can make some pretty cool stuff! Unfortunately, as of the time of writing I temporarily cannot generate these plots. :( Later diagrams that are not computer generated are drawn in Inkscape and hopefully look pretty clean.

\pagebreak

\input{preliminaries.tex}

\pagebreak

\input{holomorph.tex}

\pagebreak


\end{document}